Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-04-30 article-models-tt.tex
edited the subsubsection of substitution

The table below indicates where
we can find the axioms of each of the combinations of operators. The reference
at the row of operation $X$ and the column of operation $Y$ refers to the
axiom which explains $Y$ distributes over the arguments of $X$ when $Y$ is
applied after $X$. The empty context has no arguments, whereas extension,
and weakening have two arguments which are both of the family-kind, substitution
has two arguments of which one is a term and the other is a family and
idenitity terms have one argument, a family.
\begin{center}
\begin{tabular}{r|rrrrr}
& emp & ext & wk & subst & id\\
\hline
empty context & \autoref{comp-00} & \autoref{comp-0e}* & \autoref{comp-0w} & \autoref{comp-0s} & \xmark \\
extension & \autoref{comp-e0}* & \autoref{comp-ee}* & \autoref{comp-ew} & \cmark & \cmark \\
weakening & \autoref{comp-w0} & \autoref{comp-we}* & \autoref{comp-ww} & \autoref{comp-sw} & \autoref{comp-wi} \\
substitution & \autoref{comp-s0} & \autoref{comp-se}* & \autoref{comp-ws} & \autoref{comp-ss} & \autoref{comp-si} \\
identity terms & \cmark & \cmark & \autoref{comp-wi} & \autoref{comp-si} & \xmark
\end{tabular}
\end{center}
Apart from references to sections where axioms are given, we also see checkmarks,
crosses, marked references and duplicated references in this table. 
The checkmarks indicate that the desired property
can be proved and need not be axiomatized. To clarify those:
\begin{itemize}
\item The identity term of the empty context is the unique term of the empty
family. Recall that we already have axiomatized in \autoref{empty} that every
term of the empty family is judgmentally equal to $\emptytm$.
\item The identity term of an extension can be explained by means of the notion
of \emph{extension on terms}. This notion is defined in \autoref{extension-on-terms}
using only identity terms and substitution. With extension on terms we can
combine a term $\jterm{\Gamma}{A}{x}$ and a term $\jterm{\Gamma}{\subst{x}{P}}{u}$
into a term $\jterm{\Gamma}{{A}{P}}{\tmext{x}{u}}$, which may be seen as the
pair consisting of $x$ and $u$. Since it is a defined notion, we will
be able to derive lots of properties for extension of terms. One of them explains
how we can see the identity term of an extension as the extension of two certain
terms, see \autoref{comp-ie}.
\item Using extension on terms we can also make sense of `fibers at an extension'
because that would exactly be the fiber at an extended term. We will see in
\autoref{comp-es} that, for instance, $\subst{\tmext{x}{u}}{Q}\jdeq\subst{u}{{x}{Q}}$
for any family $\jfam{{{\Gamma}{A}}{P}}{Q}$ and any two terms $\jterm{\Gamma}{A}{x}$
and $\jterm{\Gamma}{\subst{x}{P}}{u}$. That's a form of currying.
\end{itemize}
The spots with a \xmark simply make no sense 
{\color{red}(or do they, when the term model
is better understood (by me)?)}. The marked references point to
axioms which \emph{do} have a variant for terms, but those require the notion
of extension on terms, can be proved and therefore need not be included in our
list of compatibility axioms. In each of these sections, we give a forward
reference to the lemma in which this variant is stated and proved.

>>>>

The table below indicates where
we can find the axioms of each of the combinations of operators. The reference
at the row of operation $X$ and the column of operation $Y$ refers to the
axiom which explains $Y$ distributes over the arguments of $X$ when $Y$ is
applied after $X$. The empty context has no arguments, whereas extension,
and weakening have two arguments which are both of the family-kind, substitution
has two arguments of which one is a term and the other is a family and
idenitity terms have one argument, a family.
\begin{center}
\begin{tabular}{r|rrrrr}
& emp & ext & wk & subst & id\\
\hline
extension & \autoref{comp-ee}* & \autoref{comp-ew} & \cmark & \cmark \\
weakening & \autoref{comp-we}* & \autoref{comp-ww} & \autoref{comp-sw} & \autoref{comp-wi} \\
substitution & \autoref{comp-se}* & \autoref{comp-ws} & \autoref{comp-ss} & \autoref{comp-si} \\
identity terms & \cmark & \autoref{comp-wi} & \autoref{comp-si} & \xmark
\end{tabular}
\end{center}
Apart from references to sections where axioms are given, we also see checkmarks,
crosses, marked references and duplicated references in this table. 
The checkmarks indicate that the desired property
can be proved and need not be axiomatized. To clarify those:
\begin{itemize}
\item The identity term of the empty context is the unique term of the empty
family. Recall that we already have axiomatized in \autoref{empty} that every
term of the empty family is judgmentally equal to $\emptytm$.
\item The identity term of an extension can be explained by means of the notion
of \emph{extension on terms}. This notion is defined in \autoref{extension-on-terms}
using only identity terms and substitution. With extension on terms we can
combine a term $\jterm{\Gamma}{A}{x}$ and a term $\jterm{\Gamma}{\subst{x}{P}}{u}$
into a term $\jterm{\Gamma}{{A}{P}}{\tmext{x}{u}}$, which may be seen as the
pair consisting of $x$ and $u$. Since it is a defined notion, we will
be able to derive lots of properties for extension of terms. One of them explains
how we can see the identity term of an extension as the extension of two certain
terms, see \autoref{comp-ie}.
\item Using extension on terms we can also make sense of `fibers at an extension'
because that would exactly be the fiber at an extended term. We will see in
\autoref{comp-es} that, for instance, $\subst{\tmext{x}{u}}{Q}\jdeq\subst{u}{{x}{Q}}$
for any family $\jfam{{{\Gamma}{A}}{P}}{Q}$ and any two terms $\jterm{\Gamma}{A}{x}$
and $\jterm{\Gamma}{\subst{x}{P}}{u}$. That's a form of currying.
\end{itemize}
The spots with a \xmark simply make no sense 
{\color{red}(or do they, when the term model
is better understood (by me)?)}. The marked references point to
axioms which \emph{do} have a variant for terms, but those require the notion
of extension on terms, can be proved and therefore need not be included in our
list of compatibility axioms. In each of these sections, we give a forward
reference to the lemma in which this variant is stated and proved.
